How do changes in ex vary between countries?

### 2022-03-15 draft_paper.Rmd
local commit of draft_paper

#using flextable
myft <- flextable(stat_sig_table)
myft
myft <- theme_vanilla(myft)
myft
```
Next, let's look closer at France, Scotland, and E&Ws life expectancy at birth for males.
Jon: can we somehow include these 3 in the below to produce a graph? I tried adding into the first chunk but it does not run the later parts.

>>>>

#using flextable
myft <- flextable(stat_sig_table)
myft
myft <- theme_vanilla(myft)
myft
```

Next, let's look closer at France, Scotland, and E&Ws life expectancy at birth for males.

Jon: can we somehow include these 3 in the below to produce a graph? I tried adding into the first chunk but it does not run the later parts.
